Verifying Demonstrations

### 2017-08-02 properties.tex
Adds comments from meeting

\mode<presentation>{
\begin{idea}
  \begin{itemize}
    \item There is a mechanism that provides A\ref{CreatedAfterStart} and 
      A\ref{CreatedBeforeEnd}: a blockchain.

    \item There are also other structures, e.g.\ a directed 
      graph~\cite{BlockchainFreeCryptocurrencies}.

@@

    \item A\ref{SpatiallyRelated} can be provided by \iacf{LP}.
  \end{itemize}
\end{idea}
}
\end{frame}
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{strict partial 
  order}\footnote{%
  A relation \(<\) which is irreflexive, antisymmetric and transitive.
}.
If some objects in the set relate to known points in time, then the partial 
order allows to relate the data to the time of the event.
\Cref{SpatiallyRelated} binds the data spatially to the event.

One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
blockchain.
There are also other structures, e.g.\ a directed graph that 
converges~\cite{BlockchainFreeCryptocurrencies}.
For generality, we will use the terminology of 
\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
structure \iac{tposet}.

\begin{frame}
  \begin{question}
    What about distributed voting/polling protocols?
    A tree should give a strict partial order?
  \end{question}
  \begin{question}
    Can linear blockchains also fit in the framework of 
    \textcite{BlockchainFreeCryptocurrencies}?
    Can we generalize it?
  \end{question}
\end{frame}

\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
Then we know that they cannot have been created after the event.

\begin{frame}<presentation>
  \begin{solution}[A\ref{CreatedBeforeEnd} Created before end]
    \begin{itemize}
      \item Make the \ac{LP} part of the \ac{tposet}.
      \item The proof must've been created before it was included (duh!).
      \item (Also related to V\ref{EligibilityVerif}.)
    \end{itemize}
  \end{solution}
\end{frame}

For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
in their proofs, e.g.\ the \enquote{head} of the \ac{tposet}.
This means that they cannot create a proof and keep it for a future protest.

They can use an older value (pick one from the history of the \ac{tposet}) when 
they create their proofs.
This will only expand the interval of possible creation into the past.
This will not help their cause, as anyone will recognize that the proof could 
be created at any time in that interval.

\begin{frame}
  \mode<presentation>{
  \begin{idea}[A\ref{CreatedAfterStart} Created after start]
    \begin{itemize}
      \item Include an unpredictable value in the \ac{LP}.
      \item This could be e.g.\ the hash of the \enquote{head} of the 
        \ac{tposet}.
      \item This prevents creating proofs for future protests.
    \end{itemize}
  \end{idea}
  }

@@

  \begin{question}
    How can we do \acp{LP} with 1000s of witnesses each?
    And then 1000s of such \acp{LP}?
    Ad-hoc networks, broadcast \acp{LP}?
  \end{question}
  \begin{question}
    Why should anyone trust these witnesses?
    What are the assumptions?
    Signed over a short period of time?\footnote{%
      In a sense, if they collude they have shown support for the cause.
      As long as they are not Sybil it should be fine?
    }
  \end{question}
\end{frame}

@@

In general, protesting is very similar to voting: both are many individuals 
expressing their opinion.
Hence we desire to have similar properties of verification and privacy for 
participation in a protest as there is for voting.
In the context of (electronic) voting protocols, there are three requirements 
for verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{frame}
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
  cast is legitimate.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the cast votes.
\item\label{IndividualVerif} Individual verifiability: every voter can verify 
  that their vote is included in the result.
\end{requirements}
\end{frame}
We can translate these to the case of participation in a demonstration, then 
each vote would be replaced by a proof of participation.
To have any verifiability, we need the storage (i.e.\ blockchain) to be 
immutable.
So we need a consensus protocol which prevents malicious changes.

\begin{frame}
  \mode<presentation>{
  \begin{remark}
    \begin{itemize}
      \item For valid verification we must have an immutable blockchain.
      \item We need something like a consensus protocol to prevent malicious 
        changes.
    \end{itemize}
  \end{remark}
  }

@@

If the proofs are included in a public blockchain (as suggested in 
\cref{DataAuthenticity}), then an individual can check that their proof has 
been included in the chain.
Thus \cref{IndividualVerif} is fulfilled.

\begin{frame}
  \mode<presentation>{
  \begin{idea}[V\ref{IndividualVerif} Individual verifiability]
    \begin{itemize}
      \item Proofs are stored publicly (blockchain).
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}
  }

@@

If the blockchain is public, then anyone can download all the proofs, verify 
them (eligibility) and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.

@@

A demonstration is very different from voting in one sense: Alice must be 
physically present and that very presence shows her support for the cause.
In voting, on the other hand, Alice has multiple options which are not revealed
by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof to the blockchain, the proof must be 
unlinkable to Alice, yet, if Alice submits another proof, those two proofs must 
be linkable (due to eligibility verification, \cref{EligibilityVerif}).
E.g.\ Eve compromises Alice's device (and private keys).
Anyone can verify any proof.
With the inputs that Eve can extract from the published proof and the keys she 
can find on Alice's device, she should not be able to reproduce the same 
signatures on the proof.

>>>>

\mode<presentation>{
\begin{idea}
  \begin{itemize}
    \item There is a mechanism that provides A\ref{CreatedAfterStart} and 
      A\ref{CreatedBeforeEnd}: a block chain.

@@

    \item A\ref{SpatiallyRelated} is provided by \iacf{LP}.
  \end{itemize}
\end{idea}
}
\end{frame}
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partial 
  order}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
}.
If some objects in the set relate to known points in time, then the partial 
order allows to relate the data to the time of the event.
This allows us to \emph{authenticate the data temporally}.
\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
us to \emph{authenticate the data spatially}.

One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a block 
chain.

\begin{frame}
  \begin{question}
    Are there other structures than block chains?
    E.g.~\cite{BlockchainFreeCryptocurrencies}.
  \end{question}
  \begin{question}
    What about distributed voting/polling protocols?
    A tree should give a strict partial order?
  \end{question}
\end{frame}

\Cref{CreatedBeforeEnd} is straight-forward, we simply add the proof to the 
block chain \emph{in (time-wise) relation to the event}.
Then we know that it cannot have been created after the event.

\begin{frame}<presentation>
  \begin{solution}[A\ref{CreatedBeforeEnd} Created before end]
    \begin{itemize}
      \item Make the \ac{LP} part of the block chain.
      \item The proof must've been created before it was included (duh!).
      \item (Also related to V\ref{EligibilityVerif}.)
    \end{itemize}
  \end{solution}
\end{frame}

For \cref{CreatedAfterStart} we must include an unpredictable value in the 
proof, e.g.\ the head of the block chain.
This means that we cannot create a proof and keep it for a future protest.
This also prevents us from reusing proofs from previous protests.

\begin{frame}
  \mode<presentation>{
  \begin{idea}[A\ref{CreatedAfterStart} Created after start]
    \begin{itemize}
      \item Include an unpredictable value in the \ac{LP}.
      \item This could be e.g.\ the hash of the head of the block chain.
      \item This prevents creating proofs for future protests.
    \end{itemize}
  \end{idea}
  }

@@

  \begin{question}
    How can we do \acp{LP} with 1000s of witnesses each?
    Can we do some preprocessing?
    Ad-hoc networks, broadcast \acp{LP}?
  \end{question}
  \begin{question}
    Why should anyone trust these witnesses?
    What are the assumptions?
    Signed over a short period of time?\footnote{%
      In a sense, if they collude they have shown support for the cause.
      As long as they are not Sybil it should be fine?
    }
  \end{question}
  \begin{question}
    Trusted party for the group signatures?
  \end{question}
  \begin{question}
    Must tie credentials to something unique: phone, phone subscription?
    Cannot register twice, government control?
  \end{question}
\end{frame}

@@

In general, protesting is very similar to voting: both are many individuals 
expressing their opinion.
Hence we desire to have similar properties of verification and privacy for 
participation in a protest as there is for voting.
In the context of (electronic) voting protocols, there are three requirements 
for verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{frame}
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
  cast is legitimate.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the cast votes.
\item\label{IndividualVerif} Individual verifiability: every voter can verify 
  that their vote is included in the result.
\end{requirements}
\end{frame}
We can translate these to the case of participation in a demonstration, then 
each vote would be replaced by a proof of participation.
To have any verifiability, we need the storage (i.e.\ block chain) to be 
immutable.
So we need a consensus protocol which prevents malicious changes.

\begin{frame}
  \mode<presentation>{
  \begin{remark}
    \begin{itemize}
      \item For valid verification we must have an immutable block chain.
      \item We need something like a consensus protocol to prevent malicious 
        changes.
    \end{itemize}
  \end{remark}
  }

@@

If the proofs are included in a public block chain (as suggested in 
\cref{DataAuthenticity}), then an individual can check that their proof has 
been included in the chain.
Thus \cref{IndividualVerif} is fulfilled.

\begin{frame}
  \mode<presentation>{
  \begin{idea}[V\ref{IndividualVerif} Individual verifiability]
    \begin{itemize}
      \item Proofs are stored publicly (block chain).
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}
  }

@@

If the block chain is public, then anyone can download all the proofs, verify 
them (eligibility) and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.

@@

A demonstration is very different from voting in one sense: Alice must be 
physically present and that very presence shows her support for the cause.
In voting, on the other hand, Alice has multiple options which are not revealed
by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof to the block chain, the proof must be 
unlinkable to Alice, yet, if Alice submits another proof, those two proofs must 
be linkable (due to eligibility verification, \cref{EligibilityVerif}).
E.g.\ Eve compromises Alice's device (and private keys).
Anyone can verify any proof.
With the inputs that Eve can extract from the published proof and the keys she 
can find on Alice's device, she should not be able to reproduce the same 
signatures on the proof.
So Alice needs a long-term and a short-term credential, but she should not be 
able to create two short-term credentials to participate twice.

\begin{frame}
  \begin{question}
    How do we submit the proofs to storage?
    Voting normally uses mix-nets.
    Submit over Tor~\cite{Tor}?
  \end{question}

  \mode<presentation>{
  \begin{remark}
    Without anonymous submission we don't get vote privacy, thus no receipt 
    freeness either.
  \end{remark}
  }
\end{frame}
